---
title: "01 An exmaple,Here we go, starting SEMinR"
author: "yunan"
date: "2022-10-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(seminr)
```

Until now, in terms of user friendliness, practical features, computational performance and continuous maintenance, the the package **SEMinR** can be seen as an quite good tool to deal with the problems on  structural modeling equation or generally speaking on latent variable analysis, which is a famous topic in statistics world.




## Data

```{r}
load("D:/DataScience/stat_SEM/data/mobi.rda")
dim(mobi)

head(mobi)
```

From that we can see, the columns in the data can seen as the scores on some features. The scores can be retrieved through survey or can be modeled and normalized


## Pipeline

Briefly, there are three steps to specifying and estimating a structural equation model using SEMinR. The following example is generic to either PLS-PM or CBSEM/CFA.

### 1. Describe measurement model for each construct and its items, specifying interaction terms and other measurement features:
```{r}
# Distinguish and mix composite measurement (used in PLS-PM)
# or reflective (common-factor) measurement (used in CBSEM, CFA, and PLSc)
# - We will first use composites in PLS-PM analysis
# - Later we will convert the omposites into reflectives for CFA/CBSEM (step 3)
measurements <- constructs(
  composite("Image",        multi_items("IMAG", 1:5)),
  composite("Expectation",  multi_items("CUEX", 1:3)),
  composite("Value",        multi_items("PERV", 1:2)),
  composite("Satisfaction", multi_items("CUSA", 1:3)),
  interaction_term(iv = "Image", moderator = "Expectation")
)

```

### 2. # Distinguish and mix composite measurement (used in PLS-PM)
```{r}
# Quickly create multiple paths "from" and "to" sets of constructs  
structure <- relationships(
  paths(from = c("Image", "Expectation", "Image*Expectation"), to = "Value"),
  paths(from = "Value", to = "Satisfaction")
)
```


### 3. Put the above elements together to estimate the model using PLS-PM, CBSEM, or a CFA:

#### 3.1 PLS
```{r}

# Estimate using PLS-PM from model parts defined earlier  
pls_model <- estimate_pls(data = mobi, 
                          measurement_model = measurements, 
                          structural_model = structure)

summary(pls_model)

# note: PLS requires seperate bootstrapping for PLS path estimates
# SEMinR uses multi-core parallel processing to speed up bootstrapping
boot_estimates <- bootstrap_model(pls_model, nboot = 1000, cores = 2)
summary(boot_estimates)
```


#### 3.2 CFA

Alternatively, we could estimate our model using CBSEM, which uses the Lavaan package,We often wish to conduct a CFA of our measurement model prior to CBSEM

note: we must convert composites in our measurement model into reflective constructs for CFA/CBSEM


```{r}
cfa_model <- estimate_cfa(data = mobi, as.reflective(measurements))
summary(cfa_model)
```

#### 3.3 CBSEM
```{r}
cbsem_model <- estimate_cbsem(data = mobi, as.reflective(measurements), structure)
summary(cbsem_model)

#
```
 note: the Lavaan syntax and Lavaan fitted model can be extracted for your own specific needs

```{r}
cbsem_model$lavaan_syntax
cbsem_model$lavaan_model
```






## References
* https://cran.r-project.org/web/packages/seminr/vignettes/SEMinR.html
* Partial Least Squares Structural Equation Modeling (PLS-SEM) Using R, 2022